Software Citation Principles

### 2016-07-21 sc-principles/software-citation-principles.tex
some wording fixes at beginning of appendix B

This appendix records an edited, extended description of the use cases discussed in~\S\ref{sec:use_cases}, originally found in~\cite{SC-Use-Cases}.

>>>>

This appendix records an edited, extended description of the use cases
discussed in~\S\ref{sec:use_cases}, originally found in~\cite{SC-Use-Cases}.
This discussion is not fully complete, and in some cases, it may not be fully
self-consistent, but it is part of this paper as a record of one of the inputs
to the principles. We expect that the follow-on Software Citation
Implementation Group will further develop these use cases, including explaining
in more detail how the software citation principles can be applied
to each as part of working with the stakeholders to persuade them to actually
implement the principles in their standard workflows.
